Title Text

### 2015-12-19 paper/paper.tex
Added macro expansion combinators to the policy language.

\documentclass{sigplanconf}

@@

\begin{abstract}
This is the text of the abstract.
\end{abstract}

@@

%% Word vommit
\begin{itemize}
	\item Network configuration is hard ... ...
	\item Configs are local and distributed
	\item Difficult to express intent directly
	\item Often achieve intent through indirect means (i.e., backups through aggregation)
	\item Distributed, asynchronous, environment unknown, failures ... means difficult to consider all scenarios	
	\item Problems are compounded in inter-domain routing where other factors like peering agreements are important
	\item Wide variety of considerations: Have preferences for certain routes over others, failure resistance, backups etc
	\item On the other hand, BGP is the only widely used, policy-rich routing language
	\item Often used for intra-domain routing as well
	\item We present a new language that allows operators to directly express intent for inter and intra-domain routing policies 
		  from a centralized point of view.
	\item The language provides the operator with the abstraction that they can control all end-to-end routes that transit their 
		  network, even if the routes start and/or end outside of their network.
	\item The language consists of regular expression constraints on the set of allowed routes along with a flexible preference operator
		  that allows ranking sets of paths to enable both inter-domain routing preferences and intra-domain backup paths.
	\item A compiler takes a routing policy written in this language and synthesizes concrete, per-device configurations running BGP. 
	\item The resulting configurations are guaranteed to correctly implement the policy using the standard, distributed path vector protocol, 
		  and remain correct under all possible network failure scenarios.
	\item To enable a wider spectrum of implementable policies, we model common environment assumptions (e.g., semantics of BGP community values)
		  As sets of allowed/disallowed paths provided by a neighbor using the same regular path framework.
	\item Although we choose to target BGP for both inter and intra domain routing due to its expressiveness, our language is agnostic to any particular 
		  routing protocol. It describes only routes and their relative preferences. As such, an alternative routing protocol, such as OSPF, could 
		  be used internally. This would change the set of implementable policies.
	\item To allow for more fine-grained control over control-plane details, our language permits additional constraints on the control protocol
		  (e.g., maximum number of allowed routes, whether to use multipath etc)
	\item Advantages: Centralized configuration (no copy paste error, more concise), Synthesis (no need for gory details, e.g., community values),
		  Expressiveness (backup routing, preferences, waypointing, directly say things like no transit), 
		  Correctness: (Guaranteed to implement the policy, even under failure scenarios),
		  Verification: (Language serves as a high-level abstraction of the low-level details, so we can perform verification directly on the high-level policies)
\end{itemize}

@@

\begin{itemize}
	\item Introduce language with examples...
	\item Maybe, start with a typical AS, and show how simple it would be to implement a typical policy
	\item Another good example, would be something that combined internal backup routing with preference based 
		  entrance into the network using aggregation.
	\item Could probably show an example of the resulting config, and how it is tagging using communities, 
		  or alternatively show that it doesn't compile due to a particular failure scenario.
\end{itemize}

@@

\subsection{Syntax}
Define the grammar of the language.
Need to distinguish whether the preference operator 
appears only at the top level or not.

\subsection{Semantics} 
Give the semantics in terms of ranked paths.
Should be straightforward extension of regular expression semantics with the 
additional constraint that we take only valid topology paths and that their are no paths with 
repeated locations in the path. If preferences appear only at the top level, then it is easy to rank the paths.
One tricky point is that we care about paths starting or ending at locations that are connected to end-hosts in some way.
And we want the length of the path to be a secondary tie-breaker .
Additional assumption here should be that the prefixes are disjoint.

@@

\begin{itemize}
	\item Separate prefixes so they are disjoint (assumption) for semantics)
		  probably using BDDs where each bit is a variable is the easiest way to do this.
	\item For each prefix, build a DFA from each of the regular path constraints 
		  We do this using character classes and regular expression derivatives.
		  The accepting states are labeled with the particular preference.
	\item Build the constraint graph, which gives us valid paths through the network that satisfy one or 
		  more of the regular path constraints. We accept if we are in at least one of the accepting states 
		  for one or more of the DFAs. We take the max of the preferences for the accepting preference.
		  Add a new start and end node as well.

	\item Minimize the constraint graph by removing nodes and edges that never contribute to a solution. 
		  This is sound. Removing these makes it easier to check if things are implementable using BGP (see next point).
		  There are two ways to do this: a sound heuristic for removing edges and nodes, and a complete, but slow method for 
		  removing everything not needed.

	\item Since our policy language can express things not implementable in BGP, we need a few checks.
		  First show some examples of what the problem is: why BGP cannot make a decision. 
		  The reasons this can happen are: 
		  (1) Single best path per router - no subset of paths specified is consistent (if A goes through B and C goes through A, then C goes through B).
		  (2) Failures - Have to make a decision without knowing what failures have occurred. Must be the case that

	\item We can check for topology consistency using a sufficient condition (that works often and is very fast), 
		  and by enumerating failure scenarios using a necessary and sufficient condition (that always works but is slooooow)

	\item Finally, if we know BGP can make decision locally, then we can directly translate to local BGP configurations using 
		  information about the state machines from the neighbors. In particular, we tag (and test on) community values for the
		  corresponding state and set preferences accordingly (example will be needed)
	\item Running example will be helpful here.	
\end{itemize}

@@

\begin{itemize}
	\item Compress communities by reusing communities across routers.
	      That is, we can reuse the same community value since we know who the next hop is 
	      (e.g., if there are 4 Y nodes, then use communities 0-4 for Y)

	\item If we have the same match across all starting locations, then match only on community.
		  If we have the same match across all communities (per peer) for a location, then omit checking 
		  the community (similarly avoid tagging the community from the other point of view)
		  These mainly just make things much easier to read for a human (more natural policy).
\end{itemize}

@@

\begin{itemize}
	\item Expressiveness of the policy language (maybe a proof earlier for this)
	\item Compactness of the policy language (how verbose? likely pretty concise)
	\item Intuitiveness of the policy language (how easy is it to understand? probably make the earlier examples clear)
	\item Speed of compilation (does it take forever?)
	\item Understandability of the resulting configurations (Can humans understand them?)
	\item Some measure of the size of the resulting configurations (is this actually an issue in BGP??)
\end{itemize}

>>>>

\documentclass{paper}

@@

\begin{abstract}
TODO
\end{abstract}

@@

%% Word vommit
Why network configuration is hard:
\begin{itemize}
	\item Wide variety of considerations: Have preferences for certain routes over others, failure resistance, backups etc
	\item Configurations are implemented locally and in a distributed fashion even though network intent is global
	\item Often achieve intent through indirect means (i.e., backups through aggregation, preferences through MED, AS PATH length, local-pref values, filtering through communities)
	\item Networks are distributed, asynchronous systems where the environment can be unknown, failures can occur ... which makes it difficult to consider all scenarios
	\item Problems are compounded in inter-domain setting where factors like peering agreements and bad peer behavior need to be taken into account.
	\item Protocol-specific issues such as lack of convergence in BGP
\end{itemize}

We present a new language that allows operators to directly express and compile high-level routing policies (both inter and intra-domain) from a centralized point of view.

The language provides the operator with the abstraction that they can control the routes that all traffic through their network can take, even if the routes start and/or end in a different autonomous system.

The core language consists of regular expression constraints on the set of allowed routes along with a preference operator between routes, which is used to specify both routing preferences and backup paths.
On top of the core language, we provide a higher-level macro language to talk only about constraints on routes without specifying any particular route details.

A compiler takes a routing policy written in our language and synthesizes concrete, per-device configurations running BGP. Although the language is independent of any particular routing protocol, we target BGP due to its expressiveness, scalability, and use for both inter-domain and intra-domain routing.
The compiler either guarantees that the resulting configurations correctly implement the policy and remain correct under all possible network failure scenarios, or it returns a counterexample.
(Similar to SDN, you get centralized control, yet a distributed implementation that uses an existing, scalable, fault-tolerant protocol.)

To allow for more fine-grained control over control-plane details, our language permits additional constraints on control protocol details (e.g., maximum number of allowed routes, whether to use multipath etc).

Summary: 
	 (1) Centralized: (simpler reasoning, no copy paste error, more concise), 
	 (2) Synthesis: (no need for gory details, e.g., community values, local-pref, MED, ...),
	 (3) Expressive: (backup routing, preferences, waypointing, directly say things like no transit or cold-potato routing), 
	 (4) Correct: (implement the policy, even under all failure scenarios)

@@

Sources of bugs we fix. (It seems like the main advantage of our approach is not just fixing bugs though - it is easily describing high-level intention). 
Perhaps the best way to do this is by going through a bunch of examples in section 2 and showing how you could easily introduce bugs:

\begin{itemize}
	\item Out of sync, or copy paste errors due to replicated configs (never an issue due to centralized control)
	\item Correct filtering to ensure no undesired traffic can flow through the network (e.g., best practices, like an AS should filter customers for their prefix, are implemented automatically )
	\item Failures can easily lead to unexpected behavior (e.g., a datacenter failure scenario w/instability.)
	\item Trying to do anything interesting, like get backups correct is difficult (e.g., setting up aggregation wrong)
	\item Related to the last point, things like aggregation can introduce black holes. We have the information needed to prevent this
\end{itemize}

Possible Examples:
\begin{itemize}
	\item Basic datacenter with spine preference
	\item Simple AS that prefers customers over peers over providers
	\item Combined internal backup routing with preference based entrance into the network using aggregation.
	\item Something like cold potato routing
\end{itemize}

@@

\subsection{Syntax}
Define the grammar of each of the languages - regular language, the macro language on top of it, and maybe the IR language.

\subsection{Semantics} 
Give the semantics in terms of ranked paths.
Extension of regular expression semantics with the 
additional constraint that we take only valid topology paths and that their are no paths with 
repeated locations in the path. One tricky point is that we care about paths starting or ending at locations that are 
connected to end-hosts in some way. And we want the length of the path to be a secondary tie-breaker.

@@

\begin{itemize}
	\item Separate prefixes so they are disjoint

	\item For each prefix, build a DFA from each of the regular path constraints 
		  We do this using character classes and regular expression derivatives.
		  The accepting states are labeled with the particular preference.

	\item Build the constraint graph, which gives us valid paths through the network that satisfy one or 
		  more of the regular path constraints. We accept if we are in at least one of the accepting states 
		  for one or more of the DFAs. Add a new start and end node as well.

	\item Minimize the constraint graph by removing nodes and edges that never contribute to a solution. 
		  Required for soundness. Removing these makes it easier to check if things are implementable using BGP (see next point).
		  We use several heuristics to make this faster (e.g., removing edges for dominated nodes)

	\item Since our policy language can express things not implementable in BGP, we need a few checks.
		  First show some examples of what the problem is: why BGP cannot make a decision. 
		  The reasons this can happen are: 
		  (1) Single best path per router - no subset of paths specified is consistent (if A goes through B and C goes through A, then C goes through B).
		  (2) Failures - Have to make a decision without knowing what failures have occurred. Never want to prefer one peer over another and then not get a path when one was available

	\item We can check for these with a sufficient condition (that works often and is very fast),

	\item For each router, build a preference pre-order, that defines the constraints between preferences.

	\item Finally, if we know BGP can make decision locally, then we can directly translate to local BGP configurations using 
		  information about the state machines from the neighbors. In particular, we tag (and test on) community values for the
		  corresponding state and set preferences accordingly (example will be needed)

	\item Running example will be helpful here.	
\end{itemize}

@@

\begin{itemize}
	\item For performance, the main bottleneck will probably be the minimization step. We use a number of heuristics here to make this faster.
	\item For config readability and number of route maps/communities, we avoid community tagging/matching whenever possible with a number of tricks.
\end{itemize}

@@

\begin{enumerate}
	\item Expressiveness of the policy language / BGP safe part of the language (maybe a proof earlier for this)
	\item Compactness of the policy language (how verbose/concise, maybe in loc)
	\item Intuitiveness of the policy language (how easy is it to understand? Not really a good way to evaluate this other than demonstrate earlier by example)
	\item Speed of compilation (does it take forever? what are the bottlenecks)
	\item Understandability of the resulting configurations (Can humans understand them?)
	\item Some measure of the size of the resulting configurations (e.g., the number of route maps. Is this actually ever an issue in BGP?)
\end{enumerate}

\section{Future Work}

\begin{itemize}
	\item Environments: Model environments using the same framework. (e.g., no-export allows certain paths that weren't before
	\item Verification: (Language serves as a high-level abstraction of the low-level details, so we can perform verification directly on the high-level policies)
	\item OSPF: language isn't inherently tied to BGP, and could use iBGP with OSPF or some other protocol. This would require different kinds of checks though.
\end{itemize}
